Paper Summary

### 2024-10-29 Paper_Summary.Rmd
Created Figure 1a that looks similar to the Agrawal paper.

---
title: "Paper Summary"
author: "Marqus Odisho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "Paper Summary"
author: "Marqus Odisho & Sargon"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("ggplot2")
#install.packages("lme4")
#install.packages("lmerTest")
#install.packages("MuMIn")
#install.packages("MASS")
#install.packages("dplyr")
#install.packages("tidyr")
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(MASS)
library(dplyr)
library(tidyr)
```

```{r assay 1 simulation}
###Trait of Interest: Creating normally distributed female fly populations with average value corresponding to their average number of sexual interactions. Four populations corresponding to the 4 different combinations between female fly size and environment type. (small females in cages, small females in vials, large females in cages, large females in vials)

# Sample Data (replace with your actual data)
data <- data.frame(
  Environment = factor(rep(c("Vial", "Cage"), each = 2), levels = c("Vial", "Cage")),
  Size = factor(rep(c("Small", "Large"), 2), levels = c("Small", "Large")),
  Mean = c(4, 10, 6, 5),
  SD = c(1, 1, 1, 1)  # Standard deviation (replace with your actual values)
)

# Create the bar graph with error bars (Environment on x-axis)
ggplot(data, aes(x = Environment, y = Mean, fill = Size)) + scale_y_continuous(breaks=c(0,2,4,6,8,10)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), 
                width = 0.2, position = position_dodge(0.9)) +
  labs(
    title = "Random Graph Nonsense",
    x = "",
    y = "Average Number of Sexual Interactions in a 1 Minute Period",
    fill = " " 
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom",
  ) +
  scale_fill_manual(values = c("#B6D0E2", "#F1E3D3"))  # Pastel blue and yellow
```
